MSB1015_Assignment 2

### 2019-09-25 MSB1015_Assignment2_SuzannetenHage.Rmd
Update MSB1015_Assignment2_SuzannetenHage.Rmd
Added conversion of all non-kelvin temperature to kelvin.

```{r}
# install.packages("WikidataQueryServiceR")
library("WikidataQueryServiceR")
#install.packages('rJava')
library('rJava')
#install.packages('rcdk')
library('rcdk')
#install.packages('pls')
library(pls)

@@

descriptors <- eval.desc(parsed_smiles, descNames)

>>>>

```{r}
# install.packages("WikidataQueryServiceR")
library("WikidataQueryServiceR")
#install.packages('rJava')
library('rJava')
#install.packages('rcdk')
library('rcdk')
#install.packages('pls')
library('pls')

@@

descriptors <- eval.desc(parsed_smiles, descNames)
```

**4. Data pre-processing**
Not all boiling points in the database are in kelvin, which is the SI unit for temperature. Before I continue, I make sure all temperatures are in kelvin.

```{r}
#Find all rownumbers of the values in Celcius. 
celcius <-  which(grepl('degree Celsius', data$bpUnitLabel))
for (i in 1:length(celcius)) {
  #Convert the value to kelvin
  data$bp[celcius[i]] <- data$bp[celcius[i]] + 273.15
  #Convert the label to kelvin. 
  data$bpUnitLabel[celcius[i]] <- 'kelvin'
}

#Find all rownumbers of the values in Fahrenheit. 
fahrenheit <- which(grepl('degree Fahrenheit', data$bpUnitLabel))
for (i in 1:length(fahrenheit)) {
  #Convert the value to kelvin
  data$bp[fahrenheit[i]] <- (data$bp[fahrenheit[i]] + 459.67) * (5/9)
  #Convert the label to kelvin. 
  data$bpUnitLabel[fahrenheit[i]] <- 'kelvin'
}
